\Title

### 2015-08-23 moho-inversion.tex
Initial text for methodology, GJI style files

\documentclass[]{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mbf}[1]{\mathbf{{#1}}}

@@

% Document metadata
% =================
\newcommand{\Title}{
    Non-linear gravity inversion in spherical coordinates:
    application to the South American Moho
}
\newcommand{\Keywords}{
        Moho;
        gravity inversion;
        spherical coordinates;
        tesseroid;
        South America
}
\title{\Title}
\author{
    Leonardo Uieda \\ \texttt{leo@leouieda.com}
    \and
    Val\'eria C. F. Barbosa
}

@@

\maketitle

@@

@@

Remove the Normal Earth from observations to get disturbance.
Remove topography using Bouguer and correct crustal sources.
Leaves the relief of the Moho undulating around the Normal Earth Moho
(reference level).
Reference level is the Moho of the Normal Earth.

@@

@@

\newpage
\listoftodos[Notes]

>>>>

%\documentclass[]{article}
%\usepackage{natbib}
\documentclass[extra,mreferee]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\newcommand{\mbf}[1]{\mathbf{{#1}}}

@@

% Document metadata
% =================
\newcommand{\Title}{
    Non-linear gravity inversion in spherical coordinates:
    application to the South American Moho
}
\newcommand{\Keywords}{
        Moho;
        gravity inversion;
        spherical coordinates;
        tesseroid;
        South America
}
\title[]{\Title}
\author[]{
    Leonardo Uieda$^{1,2}$,
    Valéria C. F. Barbosa$^{2}$
    \\
    $^1$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.
    e-mail: leo@leouieda.com
    \\
    $^2$Observatório Nacional, Rio de Janeiro, Brazil.
}

@@

%\label{firstpage}
\maketitle

@@

We must first isolate the target anomalous density distribution.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the gravity\footnote{The term ``gravity''
refers the sum of the gravitational and centripetal accelerations.}
of an ellipsoidal Earth (the Normal Earth or reference ellipsoid).
This is done using the formula presented in \citet{li_ellipsoid_2001}.
The resulting quantity is known as the gravity disturbance,

\begin{equation}
    \delta g(P) = g(P) - \gamma(P)
\end{equation}

\noindent in which $g(P)$ is the measured gravity at an observation point $P$
and $\gamma(P)$ is the gravity of the Normal Earth (the Normal Gravity)
calculated on point $P$.

We assume that the crust of our Normal Earth has a standard density of
$\rho_{crust} = 2670\ kg.m^{-3}$ and depth $z_{ref}$.
The disturbance contains only the gravitational effects of density
distributions that are anomalous with respect to the Normal Earth.
This includes all masses above the surface of the ellipsoid (the topography),
the mass deficiency of the oceans,
the mass deficiency of sedimentary basins,
crustal sources (e.g., igneous intrusions, lateral density changes, etc),
heterogeneities below the upper mantle,
and
the mass excesses and deficiencies caused by differences between the real Moho
topography and the reference Moho ($z_{ref}$).
The last is what we are interested in.
All effects must either be removed or assumed negligible.
The input data for the inversion is assumed to be the isolated gravitational
effect of the anomalous Moho.

@@

@@

Meh.

@@
